\begin{thebibliography}{2013}

%\bibitem{HeddenLivRub}
%M. Hedden, C. Livingston, and D. Ruberman. {Topologically slice knots with %nontrivial {A}lexander polynomial}. math/GT/1001.1538v2


\bibitem{BoyerGordonWatson}
S. Boyer, C. McA. Gordon, and L. Watson. {On L-spaces and left-orderable fundamental groups}. Mathematische Annalen. August 2013, Volume 356, Issue 4, 1213-1245.

\bibitem{CalegariDunfield}
D. Calegari and N. M. Dunfield. {Laminations and groups of homeomorphisms of the circle}. Inventiones Mathematicae. April 2003, Volume 152, Issue 1, 149-204.

\bibitem{ClayRolfsen}
A. Clay and D. Rolfsen. {Ordered Groups and Topology}. In preparation.

\bibitem{GreeneJ}
J. E. Greene. {A spanning tree model for the Heegaard Floer homology of a branched double-cover}. London Mathematical Society. Journal of Topology 6 (2013) 525-567.

\bibitem{GreeneJE}
J. E. Greene. {Alternating links and left-orderability}. arXiv:1107.5232 [math.GT]

\bibitem{GreeneWatson}
J. E. Greene, and L. Watson. {Turaev torsion, definite 4-manifolds, and quasi-alternating knots}. arXiv:1106.5559v1 [math.GT]

\bibitem{HoffmanWalsh}
N. Hoffman and G. Walsh. {Big Dehn surgery space and the link of $S^3$}. In preparation.

\bibitem{Ito}
T. Ito. {Non-left-orderable double branched coverings}. Algebraic and Geometric Topology 13 (2013) 1937-1965.

\bibitem{ManolescuOzsvath}
C. Manolescu, P. Ozsv\'{a}th. {On the Khovanov and knot Floer homologies of quasi-alternating links}. Proceedings of G\"{o}kova Geometry-Topology Conference 2007, 60–81, G\"{o}kova Geometry/Topology Conference (GGT), G\"{o}kova, 2008.

\bibitem{OS3}
P. Ozv\'{a}th and Z. Szab\'{o}. {Holomorphic disks and genus bounds}. Geom. Topol. 8 (2004), 311-334.

\bibitem{OS2}
P. Ozsv\'{a}th and Z. Szab\'{o}. {Holomorphic disks and three-manifold
invariants: Properties and applications}. Annals of Mathematics, (2) 159 (2004), no. 3, 1159-1245.

\bibitem{OzsvathSzabo}
P. Ozsv\'{a}th and Z. Szab\'{o}. {Holomorphic disks and topological invariants for closed three-manifolds.} Annals of Mathematics, (2) 159 (2004), no. 3, 1027-1158.

\bibitem{OS4}
P. Ozsv\'{a}th and Z. Szab\'{o}. {On Heegaard diagrams and holomorphic disks}. European Congress of Mathematics,
Eur. Math. Soc., Z\"{u}rich, 2005, 769-781.

\bibitem{OzsvathandSzabo}
P. Ozsv\'{a}th and Szab\'{o}. {On the Heegaard Floer homology of branched double-covers}, Adv. Math. 194 (2005) 1–33.

\end{thebibliography}
$\;$\\
\noindent{}{\sc{Department of Mathematics, Columbia University, 2990 Broadway, New York, NY 10027.}}\\
\emph{E-mail address:} {\texttt{fsd2108@columbia.edu}}
\\\\
\noindent{}{\sc{Department of Mathematics, Columbia University, 2990 Broadway, New York, NY 10027.}}\\
\emph{E-mail address:} {\texttt{mvj2110@columbia.edu}}
\\\\
\noindent{}{\sc{Department of Mathematics, Columbia University, 2990 Broadway, New York, NY 10027.}}\\
\emph{E-mail address:} {\texttt{jar2262@columbia.edu}}
\\\\
\noindent{}{\sc{Department of Mathematics, Barnard College, 333 Milbank Hall, New York, NY 10027.}}\\
\emph{E-mail address:} {\texttt{hlz2103@barnard.edu}}